Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

We now prove the first claim of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. By the earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ must be a point covered by each of $r_1',..., r_{k-2}'$. This suggests that the point is in $\bigcap_{i = 1}^{k-2}r_i'$, which thus cannot be empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

>>>>

We now prove the first claim of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. According to our earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ is a point covered by each of $r_1',..., r_{k-2}'$. Hence, $\bigcap_{i = 1}^{k-2}r_i'$ cannot be empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.
